Brief notes on erosion

### 2019-11-20 docs/proposals/NSF/ProjDocs/funding_NM.tex
NM

\pagestyle{fancy}
\lhead{\footnotesize Bryan Quaife}
\chead{\footnotesize Current and Pending Support}
\rhead{\footnotesize \thepage{ of }\pageref{LastPage}}
\cfoot{}

@@

\subsection*{Current Support:}
{\bf Title}: Computational Methods for Complex Stokesian Fluids \\
{\bf Source}: Simons Foundation, Mathematics and Physical
Sciences-Collaboration Grants for Mathematicians \\
{\bf Total Award Amount:} \$25,200 (Travel funds only) \\
{\bf Duration:} September 1, 2017--August 31, 2020 \\
{\bf Person-Months Per Year Committed to Project:} Calendar: 0,
Academic: 0, Summer: 0 \\

\noindent
{\bf Title}: The Role of Vorticity and Fuel Moisture on the Near-Field
Plume Structure and Ember Dynamics \\
{\bf Source}: Department of Defense, Strategic Environmental Research
and Development Program \\
{\bf Total Award Amount:} \$2,235,917 \\
{\bf Duration:} May 2020--January 2024 (This is a collaborative grant
that supports 7 PIs from 4 institutions) \\
{\bf Person-Months Per Year Committed to Project:} Calendar: 0,
Academic: 0, Summer: 1 \\

\vspace{-17pt}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Pending Support:}
{\bf Title}: Erosion, Transport, and Dispersion in Granular and Porous
Media (this proposal) \\
{\bf Source}: National Science Foundation, Division of Mathematical
Sciences, Computational Mathematics \\
{\bf Total Award Amount:} \$383,086 \\
{\bf Duration:} July 1, 2020--June 30, 2023 \\
{\bf Person-Months Per Year Committed to Project:} Calendar: 0,
Academic: 0, Summer: 1 \\

>>>>

\pagestyle{fancy}
\lhead{\footnotesize MNJ Moore}
\chead{\footnotesize Current and Pending Support}
\rhead{\footnotesize \thepage{ of }\pageref{LastPage}}
\cfoot{}

@@

\subsection*{Current Support:}

{\bf Title}: Dynamic interactions between fluid flows and moving boundaries \\
{\bf Source}: Simons Foundation, Mathematics and Physical
Sciences-Collaboration Grants for Mathematicians \\
{\bf Total Award Amount:} \$42,000 (Travel funds only) \\
{\bf Duration:} September 1, 2017--August 31, 2022 \\
{\bf Person-Months Per Year Committed to Project:} Calendar: 0,
Academic: 0, Summer: 0 \\

\noindent
{\bf Title}:  A Comprehensive Experimental And Computational Fluid Dynamics Analysis Of Coning In Non-Newtonian Tailings During Extraction From Tailings Ponds \\
{\bf Source}:  Institute for Oil Sands Innovation\\
{\bf Total Award Amount:} \$171,842 \\
{\bf Duration:}  January 1, 2020--January 1, 2022\\
{\bf Person-Months Per Year Committed to Project:} Calendar: 0,
Academic: 0, Summer: 0.5 \\

%\vspace{-17pt}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Pending Support:}
{\bf Title}: Erosion, Transport, and Dispersion in Granular and Porous
Media (this proposal) \\
{\bf Source}: National Science Foundation, Division of Mathematical
Sciences, Computational Mathematics \\
{\bf Total Award Amount:} \$383,086 \\
{\bf Duration:} July 1, 2020--June 30, 2023 \\
{\bf Person-Months Per Year Committed to Project:} Calendar: 0,
Academic: 0, Summer: 1 \\
